Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-06-27 reviews/methods1.Rmd
move some arguments to a later point

> We respectfully disagree.
> What makes the arguments "Bayesian" is what we take probabilities to mean.
> For a Bayesian, they represent degrees of belief.
> For a frequentist, they represent (relative) frequencies of events that result from a random process.
This is a subtle but most important distinction.
> The Bayesian position deals with what agents (here "researchers") ought to believe, assuming they are rational.
> However, even here, there is no universally agreed upon function that maps evidence onto belief (indeed, there can not be).
> We tried to make this even clearer and more explicit as to why we include several functions (and that our reasoning applies to all possible functions satisfying our assumptions).
> The frequentist understanding of probability refers strictly to statistical procedures.
> From this position, one must either argue that preregistration is changing the underlying random process/ statistical procedure or trace the impact of preregistration via indirect paths outside of the core philosophy of frequentism.
> Mayo's severity perspective is taking one more step in this direction by asserting that belief in a hypothesis is justified to the extent that it survives stringent scrutiny.
> However, even this "strong" severity principle is only a proportional statement.
> Faced with a specific tradeoff, e.g., is a particular post hoc change of a preregistration beneficial, we must revert to vague notions and "gut" instinct under this philosophy.
> Within the Bayesian framework, we may directly ask: What consequences should preregistration have on the beliefs of individual scientists or the research community as a whole?

@@

> It is well known that the math for frequentists is similar or even identical to Bayesian under the right conditions.
> Still, a frequentist would not conclude anything about the probability of H1.
> However, our goal is to say something about how preregistration changes how believable researchers should find claims made in the literature.

@@

> We find that it adds value by making an otherwise implicit process explicit to the point of calculatable.
> By conceptualising uncertainty with a specific distribution, we rid ourselves of vague notions of transparency, control, or exploration.
> This is of utmost importance because only this clarity enables us to effectively navigate the tradeoffs involved.

@@

> We agree that this argument could perhaps be made for a frequentist as well.
> However, it is not the math of the likelihood ratio that eludes us; it is how a significant result of a statistical test changes how a frequentist judges a hypothesis.
> There is a great, yet unresolved, debate in frequentism about how to do just this.
> In a Fisherian approach, no heat is paid to the power of a test; only the p-value is interpreted as the strength of evidence against the null.
> In the Neyman-Person paradigm, a decision is to be made about rejecting one or the other hypothesis.
> Mayo's severe testing returns to a gradual inference (instead of a decision) by evaluating the extent of evidence in favour of H as the extent to which a test was capable of showing that H is false.

@@

> We took considerable time to put what we meant on paper.
> In the revision, we tried hard to be clearer that uncertainty always refers to the uncertainty of the reader.
> However, being content with claiming that readers have to judge for themselves what the theoretical risk/severity of a test results in a weak argument for preregistration.
> We go further and show that for all individual assessments, preregistration has a benefit and that if one is willing to assume some parameters, this benefit is striking.

@@

> Our claim is that uncertainty is reduced, not theoretical risk directly.
> We claim that there are exploratory methods with a well-known error rate.
> For example, a neural network has extreme flexibility in fitting the data closely, yet it is calculatable.

@@

> We explicitly consider the whole space of possible measures. From the revised paper:
> *The goal is therefore to reason about the space of possible measures researchers might apply.*
> *However, since any measure fulfilling the statistical relevancy condition increases monotonically with an increase in posterior probability $P(H|E)$, we might well take it to illustrate our reasoning.*
> Later in the paper: *Of course, the assigned probabilities and the distribution $Q$ vary from study to study and researcher to researcher (and even the measure of confirmation), but we can illustrate the effect of uncertainty with an example.*

@@

> We included a section called "Hacking, harking, and other harms", which hopefully makes our thinking on these things clearer.

@@

> Absolutely. However, note that our H is always the research hypothesis, independent of the statistical H1 or H0.
> If a researcher wants to provide evidence for a null hypothesis, this is their H, theoretical risk, then is related to power.
> From the revised paper:
> *In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling, where the roles of detectability, theoretical risk and type-I/II error rate switch.*
> We reference the ideas of frequentist null hypothesis testing to provide readers who are more familiar with this line of reasoning with a better intuition, not to claim equivalent.

>>>>

> We respectfully disagree.
> What makes the arguments "Bayesian" is our interpretation of probabilities.
> For a Bayesian, they represent degrees of belief.
> For a frequentist, they represent (relative) frequencies of events that result from a random process.
> This is a subtle but most important distinction.

@@

> It is well known that the math for frequentists is similar or even identical to Bayesian under the right conditions.
> Still, a frequentist would not conclude anything about the probability of H1.
> However, our goal is to say something about how preregistration changes how believable researchers should find claims made in the literature.
> This necessitates a Bayesian perspective on the process of scientific inquiry (which we adopted) yet it applies to cases of researchers either using frequentist and Bayesian inference in their daily routine.

@@

> We find that it adds value by making an otherwise implicit process (that is, the process of updating beliefs in the theories) explicit to the point of making it calculable.
To our knowledge, there is no other perspective in the literature that makes this part of the process explicit.
> By conceptualising uncertainty with a specific distribution, we rid ourselves of vague notions of transparency, control, or exploration.
> This is of utmost importance because only this clarity enables us to effectively navigate the tradeoffs involved.

@@

> We agree that this argument could perhaps be made for a frequentist as well.
> However, it is not the math of the likelihood ratio that eludes us; it is how a significant result of a statistical test changes how a frequentist judges a hypothesis.
> There is a great, yet unresolved, debate in frequentism about how to do just this.
> In a Fisherian approach, no heat is paid to the power of a test; only the p-value is interpreted as the strength of evidence against the null.
> In the Neyman-Person paradigm, a decision is to be made about rejecting one or the other hypothesis.
> Mayo's severe testing returns to a gradual inference (instead of a decision) by evaluating the extent of evidence in favour of H as the extent to which a test was capable of showing that H is false.
> The Bayesian position deals with what agents (here "researchers") ought to believe, assuming they are rational.
> However, even here, there is no universally agreed upon function that maps evidence onto belief (indeed, there can not be).
> We tried to make this even clearer and more explicit as to why we include several functions (and that our reasoning applies to all possible functions satisfying our assumptions).
> The frequentist understanding of probability refers strictly to statistical procedures.
> From this position, one must either argue that preregistration is changing the underlying random process/ statistical procedure or trace the impact of preregistration via indirect paths outside of the core philosophy of frequentism.
> Mayo's severity perspective is taking one more step in this direction by asserting that belief in a hypothesis is justified to the extent that it survives stringent scrutiny.
> However, even this "strong" severity principle is only a proportional statement.
> Faced with a specific tradeoff, e.g., is a particular post hoc change of a preregistration beneficial, we must revert to vague notions and "gut" instinct under this philosophy.
> Within the Bayesian framework, we may directly ask: What consequences should preregistration have on the beliefs of individual scientists or the research community as a whole?

@@

> In the revision, we tried hard to be clearer that uncertainty always refers to the uncertainty of the reader.
> However, being content with claiming that readers have to judge for themselves what the theoretical risk/severity of a test results in a weak argument for preregistration.
> We go further and show that for all individual assessments, preregistration has a benefit and that if one is willing to assume some parameters, this benefit is striking.

@@

> Our claim is that uncertainty is reduced, not theoretical risk directly.
> We claim that there are exploratory methods with a well-known error rate.
> For example, a neural network has extreme flexibility in fitting the data closely, yet it is calculable.

@@

> We explicitly consider the whole space of possible measures.
> We tried to clarify this.
> Quoting From the revised paper:
> *The goal is therefore to reason about the space of possible measures researchers might apply.*
> *However, since any measure fulfilling the statistical relevancy condition increases monotonically with an increase in posterior probability $P(H|E)$, we might well take it to illustrate our reasoning.*
> Later in the paper: *Of course, the assigned probabilities and the distribution $Q$ vary from study to study and researcher to researcher (and even the measure of confirmation), but we can illustrate the effect of uncertainty with an example.*

@@

> We included a section called "Hacking, harking, and other harms", which hopefully clarifies our position.

@@

> Absolutely. However, note that our H is always the research hypothesis, independent of the statistical H1 or H0.
> If a researcher wants to provide evidence for a null hypothesis, this is their H, theoretical risk, then is related to power.
> We tried to clarify this in our revision:
> *In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling, where the roles of detectability, theoretical risk and type-I/II error rate switch.*
> We reference the ideas of frequentist null hypothesis testing to provide readers who are more familiar with this line of reasoning with a better intuition, not to claim equivalent.
